Tweets

### 2020-05-29 Rmd/tweets-one.Rmd
removed code for comparing models with dift k values

```{r, recover-{{date}}}
fn <- paste0("../data/", "{{date}}", "-analyzed-tweet-ids.csv")
#fn <- paste0("../data/", "2020-05-10", "-analyzed-tweet-ids.csv")
tr_fn <- paste0("../data/", "{{date}}", "-rehydrated-tweets.rds")
#tr_fn <- paste0("../data/", "2020-05-10", "-rehydrated-tweets.rds")
if (!file.exists(tr_fn)){
  tweets <- recover_stream(path = "{{tweet_json_file}}", verbose = TRUE) 
  #tweets <- recover_stream(path = "../data/2020-05-10 12:00:01-tweets.json", verbose = TRUE) 
  id_fn <- paste0("../data/tweets-status-ids-", "{{date}}", ".csv")
  #id_fn <- paste0("../data/tweets-status-ids-", "2020-05-10", ".csv")
  tweets %>%
    dplyr::select(status_id) %>%
    readr::write_csv(path = id_fn, 
                     col_names = FALSE)
  broken_ids <- readr::read_csv("broken_tweets.txt", col_names = FALSE) %>%
    dplyr::rename(status_id = X1) %>%
    dplyr::mutate(status_id = trimws(format(status_id, scientific = FALSE)))
  ids <- readr::read_csv(id_fn, col_names = FALSE) %>%
    dplyr::rename(status_id = X1) %>%
    dplyr::mutate(status_id = as.character(status_id))
  tweets_rehydrated1 <- rtweet::lookup_tweets(statuses = ids$status_id, 
                                              parse = TRUE)
  tweets_rehydrated2 <- rtweet::lookup_tweets(statuses = broken_ids$status_id, parse = TRUE)
  tweets_rehydrated <- tweets_rehydrated1 %>%
    dplyr::bind_rows(tweets_rehydrated2)
  # save ids of tweets that we actually used
  readr::write_csv(tibble::as_tibble(tweets_rehydrated$status_id), path = fn, col_names = FALSE)
  saveRDS(tweets_rehydrated, tr_fn)
} else {
  tweets_rehydrated <- readRDS(tr_fn)
}
```

@@

```{r, lda-{{date}}}
tweets_lda <- topicmodels::LDA(tweets_dtm, k = 6)
tweets_beta <- tidytext::tidy(tweets_lda, matrix = "beta")
```

@@

```{r, sleep-{{date}}}
Sys.sleep(15 * 60) # sleep for 15 minutes to allow api limits to reset
```

>>>>

```{r, recover-{{date}}}
fn <- paste0("../data/", "{{date}}", "-analyzed-tweet-ids.csv")
#fn <- paste0("../data/", "2020-05-10", "-analyzed-tweet-ids.csv")
tr_fn <- paste0("../data/", "{{date}}", "-rehydrated-tweets.rds")
#tr_fn <- paste0("../data/", "2020-05-10", "-rehydrated-tweets.rds")
sleep <- FALSE
if (!file.exists(tr_fn)){
  sleep <- TRUE
  tweets <- recover_stream(path = "{{tweet_json_file}}", verbose = TRUE) 
  #tweets <- recover_stream(path = "../data/2020-05-26 12:00:02-tweets.json", verbose = TRUE) 
  id_fn <- paste0("../data/tweets-status-ids-", "{{date}}", ".csv")
  #id_fn <- paste0("../data/tweets-status-ids-", "2020-05-26", ".csv")
  tweets %>%
    dplyr::select(status_id) %>%
    readr::write_csv(path = id_fn, 
                     col_names = FALSE)
  broken_ids <- readr::read_csv("broken_tweets.txt", col_names = FALSE) %>%
    dplyr::rename(status_id = X1) %>%
    dplyr::mutate(status_id = trimws(format(status_id, scientific = FALSE)))
  ids <- readr::read_csv(id_fn, col_names = FALSE) %>%
    dplyr::rename(status_id = X1) %>%
    dplyr::mutate(status_id = as.character(status_id))
  tweets_rehydrated1 <- rtweet::lookup_tweets(statuses = ids$status_id, 
                                              parse = TRUE)
  tweets_rehydrated2 <- rtweet::lookup_tweets(statuses = broken_ids$status_id, parse = TRUE)
  tweets_rehydrated <- tweets_rehydrated1 %>%
    dplyr::bind_rows(tweets_rehydrated2)
  # save ids of tweets that we actually used
  readr::write_csv(tibble::as_tibble(tweets_rehydrated$status_id), path = fn, col_names = FALSE)
  saveRDS(tweets_rehydrated, tr_fn)
} else {
  tweets_rehydrated <- readRDS(tr_fn)
}
```

@@

### Get beta plots

```{r, lda-{{date}}}
tweets_lda <- topicmodels::LDA(tweets_dtm, k = 10)
tweets_beta <- tidytext::tidy(tweets_lda, matrix = "beta")
```

@@

### Wait

```{r, sleep-{{date}}}
if (sleep) Sys.sleep(15 * 60) # sleep for 15 minutes to allow api limits to reset
```
